workshop

### 2022-09-13 scripts/workshop.Rmd
knit to html
change date to sys date

---
title: "workshop"
author: "Daniel Suh"
date: "2022-09-12"
output: html_document
---

@@

source(here("base","src.R"))
```

@@

```{r}
bc_cc_df <- left_join(cc_diff_df, bc_dist_df)
```

@@

```{r}
bc_cc_df %<>% mutate(diff = cc_norm-bc_dist)

>>>>

---
title: "workshop"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

source(here("base","src.R"))

library(reshape2)
```

@@

```{r}
bc_cc_df <- left_join(cc_diff_df, bc_dist_df)

bc_cc_df %<>% mutate(diff = cc_norm-bc_dist)

```

@@

```{r}
